---
title: "4.6"
author: "Greg Matesi"
date: "July 5, 2020"
output: pdf_document
---

```{r}
options(digits=4)
```

# Exercise 4.6

Suppose we collect dat afor a group of sutdents is a statisics class with variables $X_1$ = hours studied, $X_2$ = undergrad GPA, and $Y$ = receive an A. We fit a logistic regression and produce estimated coefficient, $\hat{\beta}_0=-6$, $\hat{\beta}_1 = 0.05$, $\hat{\beta}_2 = 1$.

## Estimate the probability that a student who studies for 40 hrs and has an undergrad GPA of 3.5 gets a A

 Set the coefficients
```{r}
x1 <- 40; x2 <- 3.5
b0 <- -6; b1 <- 0.05; b2 <- 1
```

Use equation (4.2).

```{r}
e <- exp(b0 + b1*x1+b2*x2)
e/(1+e)
```
The probability that this student gets an A is 0.38.


## How many hours would the student in part (a) need to study to have a 50% chance of getting an A?

Using equation (4.2) again, substitute $p(X) = 0.50$ and solve for $X_1$
```{r}
hours4A <- -(b0+b2*x2)/b1
hours4A
```

### Check answer
```{r}
x1 <- hours4A
e <- exp(b0 + b1*x1+b2*x2)
e/(1+e) == .5
```
So if the student from part (a) studies for 50 hours, they have a 50% chance of getting an A.
